Enhancement of SDR in Thessaloniki

### 2024-08-24 GHI_enh_04_investigate.tex
Commit 2024-08-24 20:10

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-10}
\end{figure}

@@

@@

\caption{ - empty caption - }\label{fig:groups-13}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-15}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-16}

\caption{ - empty caption - }\label{fig:groups-16}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-17}

\caption{ - empty caption - }\label{fig:groups-17}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-18}

\caption{ - empty caption - }\label{fig:groups-18}
\end{figure}

@@

\begin{verbatim}
2024-08-24 16:09:38.1 athan@tyler GHI_enh_04_investigate.R 1.792265 mins
\end{verbatim}

>>>>

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}

@@

@@

\caption{ - empty caption - }\label{fig:groups-10}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-13}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-15}
\end{figure}

@@

\begin{verbatim}
2024-08-24 16:34:51.8 athan@tyler GHI_enh_04_investigate.R 2.043213 mins
\end{verbatim}
